XRONOS: an open data infrastructure for archaeological chronology

### 2024-12-02 paper.qmd
Fix N for p3k14c

As of writing, c14bazAAR has `r format(nrow(filter(c14_global, source == "c14bazAAR")), big.mark = ",")` radiocarbon dates with unique laboratory identifiers (excluding those sourced from p3k14c and XRONOS), IntChron has `r format(nrow(filter(c14_global, source == "IntChron")), big.mark = ",")` (excluding those from non-archaeological contexts), and p3k14c has `r format(nrow(filter(c14_global, source == "c14bazAAR")), big.mark = ",")`.
The geographic distribution of dates from each is similar (@fig-c14-global), reflecting the large degree in overlap between the sources of each compilation.
IntChron, which in practice is currently only used to publish dates associated with the Oxford Radiocarbon Lab, has dates from more diverse contexts, but less overall.

>>>>

As of writing, c14bazAAR has `r format(nrow(filter(c14_global, source == "c14bazAAR")), big.mark = ",")` radiocarbon dates with unique laboratory identifiers (excluding those sourced from p3k14c and XRONOS), IntChron has `r format(nrow(filter(c14_global, source == "IntChron")), big.mark = ",")` (excluding those from non-archaeological contexts), and p3k14c has `r format(nrow(filter(c14_global, source == "p3k14c")), big.mark = ",")`.
The geographic distribution of dates from each is similar (@fig-c14-global), reflecting the large degree in overlap between the sources of each compilation.
IntChron, which in practice is currently only used to publish dates associated with the Oxford Radiocarbon Lab, has dates from more diverse contexts, but less overall.
